---
title: "Communication in Asset Markets - Subjects Level" 
author: "Lahav, Maymoni & Neugebauer"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 3
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '3'
    highlight: tango
---

```{r, echo= FALSE, message=FALSE,warning = FALSE}
library(tidyverse)
library(varhandle)
library(ggplot2)
library(ggpubr)
 
```

```{r, echo= FALSE, message=FALSE,warning = FALSE}
T1S1 <- read.csv(file="C:/Users/Liran/Google Drive/Study/PhD/a_peny_for_your_toughts/ztree/control/20211115/211115_0844team1.csv", header=FALSE, sep=",")
T1S2 <- read.csv(file="C:/Users/Liran/Google Drive/Study/PhD/a_peny_for_your_toughts/ztree/control/20211115/211115_0851team2.csv", header=FALSE, sep=",")
T1S3 <- read.csv(file="C:/Users/Liran/Google Drive/Study/PhD/a_peny_for_your_toughts/ztree/control/20211115/211115_0853team3.csv", header=FALSE, sep=",")
T1S4 <- read.csv(file="C:/Users/Liran/Google Drive/Study/PhD/a_peny_for_your_toughts/ztree/control/20211128/211128_1708team1.csv", header=FALSE, sep=",")
T1S5 <- read.csv(file="C:/Users/Liran/Google Drive/Study/PhD/a_peny_for_your_toughts/ztree/control/20211128/211128_1702team2.csv", header=FALSE, sep=",")
T1S6 <- read.csv(file="C:/Users/Liran/Google Drive/Study/PhD/a_peny_for_your_toughts/ztree/control/20211128/211128_1711team3.csv", header=FALSE, sep=",")
T3S1 <- read.csv(file="C:/Users/Liran/Google Drive/Study/PhD/a_peny_for_your_toughts/ztree/treatment3/20211116/211116_0845team1.csv", header=FALSE, sep=",")
T3S2 <- read.csv(file="C:/Users/Liran/Google Drive/Study/PhD/a_peny_for_your_toughts/ztree/treatment3/20211116/211116_0847team2.csv", header=FALSE, sep=",")
T3S3 <- read.csv(file="C:/Users/Liran/Google Drive/Study/PhD/a_peny_for_your_toughts/ztree/treatment3/20211116/211116_0816team3.csv", header=FALSE, sep=",")
T3S4 <- read.csv(file="C:/Users/Liran/Google Drive/Study/PhD/a_peny_for_your_toughts/ztree/treatment3/20211122/211122_0938team1.csv", header=FALSE, sep=",")
T3S5 <- read.csv(file="C:/Users/Liran/Google Drive/Study/PhD/a_peny_for_your_toughts/ztree/treatment3/20211122/211122_0924team2.csv", header=FALSE, sep=",")
T3S6 <- read.csv(file="C:/Users/Liran/Google Drive/Study/PhD/a_peny_for_your_toughts/ztree/treatment3/20211122/211122_0926team3.csv", header=FALSE, sep=",")
T4S1 <- read.csv(file="C:/Users/Liran/Google Drive/Study/PhD/a_peny_for_your_toughts/ztree/treatment4/20211114/211114_1128team1.csv", header=FALSE, sep=",")
T4S2 <- read.csv(file="C:/Users/Liran/Google Drive/Study/PhD/a_peny_for_your_toughts/ztree/treatment4/20211114/211114_1100team2.csv", header=FALSE, sep=",")
T4S3 <- read.csv(file="C:/Users/Liran/Google Drive/Study/PhD/a_peny_for_your_toughts/ztree/treatment4/20211114/211114_1109team3.csv", header=FALSE, sep=",")
T4S4 <- read.csv(file="C:/Users/Liran/Google Drive/Study/PhD/a_peny_for_your_toughts/ztree/treatment4/20211128/211128_1334team1.csv", header=FALSE, sep=",")
T4S5 <- read.csv(file="C:/Users/Liran/Google Drive/Study/PhD/a_peny_for_your_toughts/ztree/treatment4/20211128/211128_1320team2.csv", header=FALSE, sep=",")
T4S6 <- read.csv(file="C:/Users/Liran/Google Drive/Study/PhD/a_peny_for_your_toughts/ztree/treatment4/20211128/211128_1323team3.csv", header=FALSE, sep=",")
```




# HL distributions {.tabset}

## Aggregate

```{r, echo= FALSE, message=FALSE}
HL_T1S1 = unfactor(as.factor(data.frame(T1S1 %>% filter(V3=="subjects", V2==1))[c(2:7),38]))
HL_T1S2 = unfactor(as.factor(data.frame(T1S2 %>% filter(V3=="subjects", V2==1))[c(2:7),38]))
HL_T1S3 = unfactor(as.factor(data.frame(T1S3 %>% filter(V3=="subjects", V2==1))[c(2:7),38]))
HL_T1S4 = unfactor(as.factor(data.frame(T1S4 %>% filter(V3=="subjects", V2==1))[c(2:7),38]))
HL_T1S5 = unfactor(as.factor(data.frame(T1S5 %>% filter(V3=="subjects", V2==1))[c(2:7),38]))
HL_T1S6 = unfactor(as.factor(data.frame(T1S6 %>% filter(V3=="subjects", V2==1))[c(2:7),38]))
HL_T3S1 = unfactor(as.factor(data.frame(T3S1 %>% filter(V3=="subjects", V2==1))[c(2:7),38]))
HL_T3S2 = unfactor(as.factor(data.frame(T3S2 %>% filter(V3=="subjects", V2==1))[c(2:7),38]))
HL_T3S3 = unfactor(as.factor(data.frame(T3S3 %>% filter(V3=="subjects", V2==1))[c(2:7),38]))
HL_T3S4 = unfactor(as.factor(data.frame(T3S4 %>% filter(V3=="subjects", V2==1))[c(2:7),38]))
HL_T3S5 = unfactor(as.factor(data.frame(T3S5 %>% filter(V3=="subjects", V2==1))[c(2:7),38]))
HL_T3S6 = unfactor(as.factor(data.frame(T3S6 %>% filter(V3=="subjects", V2==1))[c(2:7),38]))
HL_T4S1 = unfactor(as.factor(data.frame(T4S1 %>% filter(V3=="subjects", V2==1))[c(2:7),38]))
HL_T4S2 = unfactor(as.factor(data.frame(T4S2 %>% filter(V3=="subjects", V2==1))[c(2:7),38]))
HL_T4S3 = unfactor(as.factor(data.frame(T4S3 %>% filter(V3=="subjects", V2==1))[c(2:7),38]))
HL_T4S4 = unfactor(as.factor(data.frame(T4S4 %>% filter(V3=="subjects", V2==1))[c(2:7),38]))
HL_T4S5 = unfactor(as.factor(data.frame(T4S5 %>% filter(V3=="subjects", V2==1))[c(2:7),38]))
HL_T4S6 = unfactor(as.factor(data.frame(T4S6 %>% filter(V3=="subjects", V2==1))[c(2:7),38]))

HL_agg = c()

for (t in c(1,3,4)){
for (s in 1:6){
session_num=s
treatment_num=t
mydata <- get(paste("HL_T",t,paste("S",s,sep=""),sep=""))
mydata = t(t(as.data.frame(mydata)))
session = as.data.frame(rep(session_num,6))
treatment = as.data.frame(rep(treatment_num,6))
player = as.data.frame(c(1:6))

mydata = cbind(player,mydata)
mydata = cbind(session,mydata)
mydata = cbind(treatment,mydata)

HL_agg = rbind(HL_agg,mydata)
}}
colnames(HL_agg) = c("Treatment","S","P","HL")

ggplot(HL_agg, aes(x=HL)) + 
  geom_histogram(fill="lightblue", color="grey50", binwidth=0.5)+
  ggtitle("HL Distribution (Extreme risk seeking = 10)") + 
  scale_x_continuous(name = "HL", breaks = seq(0, 10, by = 1)) + 
  scale_y_continuous(name = "Count", breaks = seq(0, 35, by = 5))


```

## Control Treatment

```{r, echo= FALSE, message=FALSE,warning = FALSE}
mydata = data.frame(HL_agg %>% filter(Treatment==1,S==1))
S1 = ggplot(mydata, aes(x=HL)) + 
  geom_histogram(fill="lightblue", color="grey50", binwidth=0.5)+
  ggtitle("Session 1") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0,10)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,4)) +
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(HL_agg %>% filter(Treatment==1,S==2))
S2 = ggplot(mydata, aes(x=HL)) + 
  geom_histogram(fill="lightblue", color="grey50", binwidth=0.5)+
  ggtitle("Session 2") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0,10)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,4))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(HL_agg %>% filter(Treatment==1,S==3))
S3 = ggplot(mydata, aes(x=HL)) + 
  geom_histogram(fill="lightblue", color="grey50", binwidth=0.5)+
  ggtitle("Session 3") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0,10)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,4))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(HL_agg %>% filter(Treatment==1,S==4))
S4 = ggplot(mydata, aes(x=HL)) + 
  geom_histogram(fill="lightblue", color="grey50", binwidth=0.5)+
  ggtitle("Session 4") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0,10)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,4))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(HL_agg %>% filter(Treatment==1,S==5))
S5 = ggplot(mydata, aes(x=HL)) + 
  geom_histogram(fill="lightblue", color="grey50", binwidth=0.5)+
  ggtitle("Session 5") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0,10)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,4))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(HL_agg %>% filter(Treatment==1,S==6))
S6 = ggplot(mydata, aes(x=HL)) + 
  geom_histogram(fill="lightblue", color="grey50", binwidth=0.5)+
  ggtitle("Session 6") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0,10)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,4))+
  rremove("ylab")+ rremove("xlab")

ggarrange(S1, S2, S3, S4, S5, S6,
                    ncol = 2, nrow = 3)
```


## Treatment 3

```{r, echo= FALSE, message=FALSE,warning = FALSE}
mydata = data.frame(HL_agg %>% filter(Treatment==3,S==1))
S1 = ggplot(mydata, aes(x=HL)) + 
  geom_histogram(fill="lightblue", color="grey50", binwidth=0.5)+
  ggtitle("Session 1") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0,10)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,4)) +
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(HL_agg %>% filter(Treatment==3,S==2))
S2 = ggplot(mydata, aes(x=HL)) + 
  geom_histogram(fill="lightblue", color="grey50", binwidth=0.5)+
  ggtitle("Session 2") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0,10)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,4))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(HL_agg %>% filter(Treatment==3,S==3))
S3 = ggplot(mydata, aes(x=HL)) + 
  geom_histogram(fill="lightblue", color="grey50", binwidth=0.5)+
  ggtitle("Session 3") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0,10)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,4))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(HL_agg %>% filter(Treatment==3,S==4))
S4 = ggplot(mydata, aes(x=HL)) + 
  geom_histogram(fill="lightblue", color="grey50", binwidth=0.5)+
  ggtitle("Session 4") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0,10)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,4))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(HL_agg %>% filter(Treatment==3,S==5))
S5 = ggplot(mydata, aes(x=HL)) + 
  geom_histogram(fill="lightblue", color="grey50", binwidth=0.5)+
  ggtitle("Session 5") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0,10)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,4))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(HL_agg %>% filter(Treatment==3,S==6))
S6 = ggplot(mydata, aes(x=HL)) + 
  geom_histogram(fill="lightblue", color="grey50", binwidth=0.5)+
  ggtitle("Session 6") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0,10)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,4))+
  rremove("ylab")+ rremove("xlab")

ggarrange(S1, S2, S3, S4, S5, S6,
                    ncol = 2, nrow = 3)
```


## Treatment 4

```{r, echo= FALSE, message=FALSE,warning = FALSE}
mydata = data.frame(HL_agg %>% filter(Treatment==4,S==1))
S1 = ggplot(mydata, aes(x=HL)) + 
  geom_histogram(fill="lightblue", color="grey50", binwidth=0.5)+
  ggtitle("Session 1") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0,10)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,4)) +
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(HL_agg %>% filter(Treatment==4,S==2))
S2 = ggplot(mydata, aes(x=HL)) + 
  geom_histogram(fill="lightblue", color="grey50", binwidth=0.5)+
  ggtitle("Session 2") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0,10)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,4))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(HL_agg %>% filter(Treatment==4,S==3))
S3 = ggplot(mydata, aes(x=HL)) + 
  geom_histogram(fill="lightblue", color="grey50", binwidth=0.5)+
  ggtitle("Session 3") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0,10)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,4))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(HL_agg %>% filter(Treatment==4,S==4))
S4 = ggplot(mydata, aes(x=HL)) + 
  geom_histogram(fill="lightblue", color="grey50", binwidth=0.5)+
  ggtitle("Session 4") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0,10)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,4))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(HL_agg %>% filter(Treatment==4,S==5))
S5 = ggplot(mydata, aes(x=HL)) + 
  geom_histogram(fill="lightblue", color="grey50", binwidth=0.5)+
  ggtitle("Session 5") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0,10)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,4))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(HL_agg %>% filter(Treatment==4,S==6))
S6 = ggplot(mydata, aes(x=HL)) + 
  geom_histogram(fill="lightblue", color="grey50", binwidth=0.5)+
  ggtitle("Session 6") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0,10)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,4))+
  rremove("ylab")+ rremove("xlab")

ggarrange(S1, S2, S3, S4, S5, S6,
                    ncol = 2, nrow = 3)
```




# CRT distributions {.tabset}

## Aggregate

```{r, echo= FALSE, message=FALSE}
CRT_T1S1 = unfactor(as.factor(data.frame(T1S1 %>% filter(V3=="subjects", V2==1))[c(2:7),61]))
CRT_T1S2 = unfactor(as.factor(data.frame(T1S2 %>% filter(V3=="subjects", V2==1))[c(2:7),61]))
CRT_T1S3 = unfactor(as.factor(data.frame(T1S3 %>% filter(V3=="subjects", V2==1))[c(2:7),61]))
CRT_T1S4 = unfactor(as.factor(data.frame(T1S4 %>% filter(V3=="subjects", V2==1))[c(2:7),61]))
CRT_T1S5 = unfactor(as.factor(data.frame(T1S5 %>% filter(V3=="subjects", V2==1))[c(2:7),61]))
CRT_T1S6 = unfactor(as.factor(data.frame(T1S6 %>% filter(V3=="subjects", V2==1))[c(2:7),61]))
CRT_T3S1 = unfactor(as.factor(data.frame(T3S1 %>% filter(V3=="subjects", V2==1))[c(2:7),61]))
CRT_T3S2 = unfactor(as.factor(data.frame(T3S2 %>% filter(V3=="subjects", V2==1))[c(2:7),61]))
CRT_T3S3 = unfactor(as.factor(data.frame(T3S3 %>% filter(V3=="subjects", V2==1))[c(2:7),61]))
CRT_T3S4 = unfactor(as.factor(data.frame(T3S4 %>% filter(V3=="subjects", V2==1))[c(2:7),61]))
CRT_T3S5 = unfactor(as.factor(data.frame(T3S5 %>% filter(V3=="subjects", V2==1))[c(2:7),61]))
CRT_T3S6 = unfactor(as.factor(data.frame(T3S6 %>% filter(V3=="subjects", V2==1))[c(2:7),61]))
CRT_T4S1 = unfactor(as.factor(data.frame(T4S1 %>% filter(V3=="subjects", V2==1))[c(2:7),61]))
CRT_T4S2 = unfactor(as.factor(data.frame(T4S2 %>% filter(V3=="subjects", V2==1))[c(2:7),61]))
CRT_T4S3 = unfactor(as.factor(data.frame(T4S3 %>% filter(V3=="subjects", V2==1))[c(2:7),61]))
CRT_T4S4 = unfactor(as.factor(data.frame(T4S4 %>% filter(V3=="subjects", V2==1))[c(2:7),61]))
CRT_T4S5 = unfactor(as.factor(data.frame(T4S5 %>% filter(V3=="subjects", V2==1))[c(2:7),61]))
CRT_T4S6 = unfactor(as.factor(data.frame(T4S6 %>% filter(V3=="subjects", V2==1))[c(2:7),61]))

CRT_agg = c()

for (t in c(1,3,4)){
for (s in 1:6){
session_num=s
treatment_num=t
mydata <- get(paste("CRT_T",t,paste("S",s,sep=""),sep=""))
mydata = t(t(as.data.frame(mydata)))
session = as.data.frame(rep(session_num,6))
treatment = as.data.frame(rep(treatment_num,6))
player = as.data.frame(c(1:6))

mydata = cbind(player,mydata)
mydata = cbind(session,mydata)
mydata = cbind(treatment,mydata)

CRT_agg = rbind(CRT_agg,mydata)
}}
colnames(CRT_agg) = c("Treatment","S","P","CRT")

ggplot(CRT_agg, aes(x=CRT)) + 
  geom_histogram(fill="lightgreen", color="grey50", binwidth=0.5)+
  ggtitle("CRT Distribution") + 
  scale_x_continuous(name = "CRT", breaks = seq(0, 10, by = 1)) + 
  scale_y_continuous(name = "Count", breaks = seq(0, 50, by = 5))


```

## Control Treatment

```{r, echo= FALSE, message=FALSE,warning = FALSE}
mydata = data.frame(CRT_agg %>% filter(Treatment==1,S==1))
S1 = ggplot(mydata, aes(x=CRT)) + 
  geom_histogram(fill="lightgreen", color="grey50", binwidth=0.5)+
  ggtitle("Session 1") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(-0.5,3.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6)) +
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(CRT_agg %>% filter(Treatment==1,S==2))
S2 = ggplot(mydata, aes(x=CRT)) + 
  geom_histogram(fill="lightgreen", color="grey50", binwidth=0.5)+
  ggtitle("Session 2") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(-0.5,3.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(CRT_agg %>% filter(Treatment==1,S==3))
S3 = ggplot(mydata, aes(x=CRT)) + 
  geom_histogram(fill="lightgreen", color="grey50", binwidth=0.5)+
  ggtitle("Session 3") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(-0.5,3.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(CRT_agg %>% filter(Treatment==1,S==4))
S4 = ggplot(mydata, aes(x=CRT)) + 
  geom_histogram(fill="lightgreen", color="grey50", binwidth=0.5)+
  ggtitle("Session 4") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(-0.5,3.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(CRT_agg %>% filter(Treatment==1,S==5))
S5 = ggplot(mydata, aes(x=CRT)) + 
  geom_histogram(fill="lightgreen", color="grey50", binwidth=0.5)+
  ggtitle("Session 5") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(-0.5,3.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(CRT_agg %>% filter(Treatment==1,S==6))
S6 = ggplot(mydata, aes(x=CRT)) + 
  geom_histogram(fill="lightgreen", color="grey50", binwidth=0.5)+
  ggtitle("Session 6") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(-0.5,3.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6))+
  rremove("ylab")+ rremove("xlab")

ggarrange(S1, S2, S3, S4, S5, S6,
                    ncol = 2, nrow = 3)
```


## Treatment 3

```{r, echo= FALSE, message=FALSE,warning = FALSE}
mydata = data.frame(CRT_agg %>% filter(Treatment==3,S==1))
S1 = ggplot(mydata, aes(x=CRT)) + 
  geom_histogram(fill="lightgreen", color="grey50", binwidth=0.5)+
  ggtitle("Session 1") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(-0.5,3.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6)) +
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(CRT_agg %>% filter(Treatment==3,S==2))
S2 = ggplot(mydata, aes(x=CRT)) + 
  geom_histogram(fill="lightgreen", color="grey50", binwidth=0.5)+
  ggtitle("Session 2") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(-0.5,3.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(CRT_agg %>% filter(Treatment==3,S==3))
S3 = ggplot(mydata, aes(x=CRT)) + 
  geom_histogram(fill="lightgreen", color="grey50", binwidth=0.5)+
  ggtitle("Session 3") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(-0.5,3.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(CRT_agg %>% filter(Treatment==3,S==4))
S4 = ggplot(mydata, aes(x=CRT)) + 
  geom_histogram(fill="lightgreen", color="grey50", binwidth=0.5)+
  ggtitle("Session 4") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(-0.5,3.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(CRT_agg %>% filter(Treatment==3,S==5))
S5 = ggplot(mydata, aes(x=CRT)) + 
  geom_histogram(fill="lightgreen", color="grey50", binwidth=0.5)+
  ggtitle("Session 5") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(-0.5,3.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(CRT_agg %>% filter(Treatment==3,S==6))
S6 = ggplot(mydata, aes(x=CRT)) + 
  geom_histogram(fill="lightgreen", color="grey50", binwidth=0.5)+
  ggtitle("Session 6") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(-0.5,3.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6))+
  rremove("ylab")+ rremove("xlab")

ggarrange(S1, S2, S3, S4, S5, S6,
                    ncol = 2, nrow = 3)
```


## Treatment 4

```{r, echo= FALSE, message=FALSE,warning = FALSE}
mydata = data.frame(CRT_agg %>% filter(Treatment==4,S==1))
S1 = ggplot(mydata, aes(x=CRT)) + 
  geom_histogram(fill="lightgreen", color="grey50", binwidth=0.5)+
  ggtitle("Session 1") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(-0.5,3.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6)) +
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(CRT_agg %>% filter(Treatment==4,S==2))
S2 = ggplot(mydata, aes(x=CRT)) + 
  geom_histogram(fill="lightgreen", color="grey50", binwidth=0.5)+
  ggtitle("Session 2") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(-0.5,3.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(CRT_agg %>% filter(Treatment==4,S==3))
S3 = ggplot(mydata, aes(x=CRT)) + 
  geom_histogram(fill="lightgreen", color="grey50", binwidth=0.5)+
  ggtitle("Session 3") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(-0.5,3.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(CRT_agg %>% filter(Treatment==4,S==4))
S4 = ggplot(mydata, aes(x=CRT)) + 
  geom_histogram(fill="lightgreen", color="grey50", binwidth=0.5)+
  ggtitle("Session 4") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(-0.5,3.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(CRT_agg %>% filter(Treatment==4,S==5))
S5 = ggplot(mydata, aes(x=CRT)) + 
  geom_histogram(fill="lightgreen", color="grey50", binwidth=0.5)+
  ggtitle("Session 5") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(-0.5,3.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(CRT_agg %>% filter(Treatment==4,S==6))
S6 = ggplot(mydata, aes(x=CRT)) + 
  geom_histogram(fill="lightgreen", color="grey50", binwidth=0.5)+
  ggtitle("Session 6") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(-0.5,3.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6))+
  rremove("ylab")+ rremove("xlab")

ggarrange(S1, S2, S3, S4, S5, S6,
                    ncol = 2, nrow = 3)
```




# Gender distributions {.tabset}

## Aggregate

```{r, echo= FALSE, message=FALSE}
Gender_T1S1 = unfactor(as.factor(data.frame(T1S1 %>% filter(V3=="subjects", V2==2, V4==15))[c(1:6),2594]))
Gender_T1S2 = unfactor(as.factor(data.frame(T1S2 %>% filter(V3=="subjects", V2==2, V4==15))[c(1:6),2594]))
Gender_T1S3 = unfactor(as.factor(data.frame(T1S3 %>% filter(V3=="subjects", V2==2, V4==15))[c(1:6),2594]))
Gender_T1S4 = unfactor(as.factor(data.frame(T1S4 %>% filter(V3=="subjects", V2==2, V4==15))[c(1:6),2594]))
Gender_T1S5 = unfactor(as.factor(data.frame(T1S5 %>% filter(V3=="subjects", V2==2, V4==15))[c(1:6),2594]))
Gender_T1S6 = unfactor(as.factor(data.frame(T1S6 %>% filter(V3=="subjects", V2==2, V4==15))[c(1:6),2594]))
Gender_T3S1 = unfactor(as.factor(data.frame(T3S1 %>% filter(V3=="subjects", V2==2, V4==15))[c(1:6),2566]))
Gender_T3S2 = unfactor(as.factor(data.frame(T3S2 %>% filter(V3=="subjects", V2==2, V4==15))[c(1:6),2566]))
Gender_T3S3 = unfactor(as.factor(data.frame(T3S3 %>% filter(V3=="subjects", V2==2, V4==15))[c(1:6),2566]))
Gender_T3S4 = unfactor(as.factor(data.frame(T3S4 %>% filter(V3=="subjects", V2==2, V4==15))[c(1:6),2566]))
Gender_T3S5 = unfactor(as.factor(data.frame(T3S5 %>% filter(V3=="subjects", V2==2, V4==15))[c(1:6),2566]))
Gender_T3S6 = unfactor(as.factor(data.frame(T3S6 %>% filter(V3=="subjects", V2==2, V4==15))[c(1:6),2566]))
Gender_T4S1 = unfactor(as.factor(data.frame(T4S1 %>% filter(V3=="subjects", V2==2, V4==15))[c(1:6),2594]))
Gender_T4S2 = unfactor(as.factor(data.frame(T4S2 %>% filter(V3=="subjects", V2==2, V4==15))[c(1:6),2594]))
Gender_T4S3 = unfactor(as.factor(data.frame(T4S3 %>% filter(V3=="subjects", V2==2, V4==15))[c(1:6),2594]))
Gender_T4S4 = unfactor(as.factor(data.frame(T4S4 %>% filter(V3=="subjects", V2==2, V4==15))[c(1:6),2594]))
Gender_T4S5 = unfactor(as.factor(data.frame(T4S5 %>% filter(V3=="subjects", V2==2, V4==15))[c(1:6),2594]))
Gender_T4S6 = unfactor(as.factor(data.frame(T4S6 %>% filter(V3=="subjects", V2==2, V4==15))[c(1:6),2594]))

Gender_agg = c()

for (t in c(1,3,4)){
for (s in 1:6){
session_num=s
treatment_num=t
mydata <- get(paste("Gender_T",t,paste("S",s,sep=""),sep=""))
mydata = t(t(as.data.frame(mydata)))
session = as.data.frame(rep(session_num,6))
treatment = as.data.frame(rep(treatment_num,6))
player = as.data.frame(c(1:6))

mydata = cbind(player,mydata)
mydata = cbind(session,mydata)
mydata = cbind(treatment,mydata)

Gender_agg = rbind(Gender_agg,mydata)
}}
colnames(Gender_agg) = c("Treatment","S","P","Gender")

ggplot(Gender_agg, aes(x=Gender)) + 
  geom_histogram(fill="orange", color="grey50", binwidth=0.5)+
  ggtitle("Gender Distribution (Female=1)") + 
  scale_x_continuous(name = "Gender", breaks = seq(0, 10, by = 1)) + 
  scale_y_continuous(name = "Count", breaks = seq(0, 100, by = 10))


```

## Control Treatment

```{r, echo= FALSE, message=FALSE,warning = FALSE}
mydata = data.frame(Gender_agg %>% filter(Treatment==1,S==1))
S1 = ggplot(mydata, aes(x=Gender)) + 
  geom_histogram(fill="orange", color="grey50", binwidth=0.5)+
  ggtitle("Session 1") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0.5,7.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6)) +
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(Gender_agg %>% filter(Treatment==1,S==2))
S2 = ggplot(mydata, aes(x=Gender)) + 
  geom_histogram(fill="orange", color="grey50", binwidth=0.5)+
  ggtitle("Session 2") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0.5,7.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(Gender_agg %>% filter(Treatment==1,S==3))
S3 = ggplot(mydata, aes(x=Gender)) + 
  geom_histogram(fill="orange", color="grey50", binwidth=0.5)+
  ggtitle("Session 3") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0.5,7.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(Gender_agg %>% filter(Treatment==1,S==4))
S4 = ggplot(mydata, aes(x=Gender)) + 
  geom_histogram(fill="orange", color="grey50", binwidth=0.5)+
  ggtitle("Session 4") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0.5,7.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(Gender_agg %>% filter(Treatment==1,S==5))
S5 = ggplot(mydata, aes(x=Gender)) + 
  geom_histogram(fill="orange", color="grey50", binwidth=0.5)+
  ggtitle("Session 5") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0.5,7.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(Gender_agg %>% filter(Treatment==1,S==6))
S6 = ggplot(mydata, aes(x=Gender)) + 
  geom_histogram(fill="orange", color="grey50", binwidth=0.5)+
  ggtitle("Session 6") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0.5,7.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6))+
  rremove("ylab")+ rremove("xlab")

ggarrange(S1, S2, S3, S4, S5, S6,
                    ncol = 2, nrow = 3)
```


## Treatment 3

```{r, echo= FALSE, message=FALSE,warning = FALSE}
mydata = data.frame(Gender_agg %>% filter(Treatment==3,S==1))
S1 = ggplot(mydata, aes(x=Gender)) + 
  geom_histogram(fill="orange", color="grey50", binwidth=0.5)+
  ggtitle("Session 1") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0.5,7.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6)) +
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(Gender_agg %>% filter(Treatment==3,S==2))
S2 = ggplot(mydata, aes(x=Gender)) + 
  geom_histogram(fill="orange", color="grey50", binwidth=0.5)+
  ggtitle("Session 2") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0.5,7.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(Gender_agg %>% filter(Treatment==3,S==3))
S3 = ggplot(mydata, aes(x=Gender)) + 
  geom_histogram(fill="orange", color="grey50", binwidth=0.5)+
  ggtitle("Session 3") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0.5,7.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(Gender_agg %>% filter(Treatment==3,S==4))
S4 = ggplot(mydata, aes(x=Gender)) + 
  geom_histogram(fill="orange", color="grey50", binwidth=0.5)+
  ggtitle("Session 4") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0.5,7.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(Gender_agg %>% filter(Treatment==3,S==5))
S5 = ggplot(mydata, aes(x=Gender)) + 
  geom_histogram(fill="orange", color="grey50", binwidth=0.5)+
  ggtitle("Session 5") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0.5,7.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(Gender_agg %>% filter(Treatment==3,S==6))
S6 = ggplot(mydata, aes(x=Gender)) + 
  geom_histogram(fill="orange", color="grey50", binwidth=0.5)+
  ggtitle("Session 6") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0.5,7.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6))+
  rremove("ylab")+ rremove("xlab")

ggarrange(S1, S2, S3, S4, S5, S6,
                    ncol = 2, nrow = 3)
```


## Treatment 4

```{r, echo= FALSE, message=FALSE,warning = FALSE}
mydata = data.frame(Gender_agg %>% filter(Treatment==4,S==1))
S1 = ggplot(mydata, aes(x=Gender)) + 
  geom_histogram(fill="orange", color="grey50", binwidth=0.5)+
  ggtitle("Session 1") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0.5,7.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6)) +
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(Gender_agg %>% filter(Treatment==4,S==2))
S2 = ggplot(mydata, aes(x=Gender)) + 
  geom_histogram(fill="orange", color="grey50", binwidth=0.5)+
  ggtitle("Session 2") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0.5,7.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(Gender_agg %>% filter(Treatment==4,S==3))
S3 = ggplot(mydata, aes(x=Gender)) + 
  geom_histogram(fill="orange", color="grey50", binwidth=0.5)+
  ggtitle("Session 3") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0.5,7.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(Gender_agg %>% filter(Treatment==4,S==4))
S4 = ggplot(mydata, aes(x=Gender)) + 
  geom_histogram(fill="orange", color="grey50", binwidth=0.5)+
  ggtitle("Session 4") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0.5,7.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(Gender_agg %>% filter(Treatment==4,S==5))
S5 = ggplot(mydata, aes(x=Gender)) + 
  geom_histogram(fill="orange", color="grey50", binwidth=0.5)+
  ggtitle("Session 5") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0.5,7.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(Gender_agg %>% filter(Treatment==4,S==6))
S6 = ggplot(mydata, aes(x=Gender)) + 
  geom_histogram(fill="orange", color="grey50", binwidth=0.5)+
  ggtitle("Session 6") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0.5,7.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6))+
  rremove("ylab")+ rremove("xlab")

ggarrange(S1, S2, S3, S4, S5, S6,
                    ncol = 2, nrow = 3)
```




# Risk Taking distributions {.tabset}

## Aggregate

```{r, echo= FALSE, message=FALSE}
Risk_T1S1 = unfactor(as.factor(data.frame(T1S1 %>% filter(V3=="subjects", V2==2, V4==15))[c(1:6),2589]))
Risk_T1S2 = unfactor(as.factor(data.frame(T1S2 %>% filter(V3=="subjects", V2==2, V4==15))[c(1:6),2589]))
Risk_T1S3 = unfactor(as.factor(data.frame(T1S3 %>% filter(V3=="subjects", V2==2, V4==15))[c(1:6),2589]))
Risk_T1S4 = unfactor(as.factor(data.frame(T1S4 %>% filter(V3=="subjects", V2==2, V4==15))[c(1:6),2589]))
Risk_T1S5 = unfactor(as.factor(data.frame(T1S5 %>% filter(V3=="subjects", V2==2, V4==15))[c(1:6),2589]))
Risk_T1S6 = unfactor(as.factor(data.frame(T1S6 %>% filter(V3=="subjects", V2==2, V4==15))[c(1:6),2589]))
Risk_T3S1 = unfactor(as.factor(data.frame(T3S1 %>% filter(V3=="subjects", V2==2, V4==15))[c(1:6),2561]))
Risk_T3S2 = unfactor(as.factor(data.frame(T3S2 %>% filter(V3=="subjects", V2==2, V4==15))[c(1:6),2561]))
Risk_T3S3 = unfactor(as.factor(data.frame(T3S3 %>% filter(V3=="subjects", V2==2, V4==15))[c(1:6),2561]))
Risk_T3S4 = unfactor(as.factor(data.frame(T3S4 %>% filter(V3=="subjects", V2==2, V4==15))[c(1:6),2561]))
Risk_T3S5 = unfactor(as.factor(data.frame(T3S5 %>% filter(V3=="subjects", V2==2, V4==15))[c(1:6),2561]))
Risk_T3S6 = unfactor(as.factor(data.frame(T3S6 %>% filter(V3=="subjects", V2==2, V4==15))[c(1:6),2561]))
Risk_T4S1 = unfactor(as.factor(data.frame(T4S1 %>% filter(V3=="subjects", V2==2, V4==15))[c(1:6),2589]))
Risk_T4S2 = unfactor(as.factor(data.frame(T4S2 %>% filter(V3=="subjects", V2==2, V4==15))[c(1:6),2589]))
Risk_T4S3 = unfactor(as.factor(data.frame(T4S3 %>% filter(V3=="subjects", V2==2, V4==15))[c(1:6),2589]))
Risk_T4S4 = unfactor(as.factor(data.frame(T4S4 %>% filter(V3=="subjects", V2==2, V4==15))[c(1:6),2589]))
Risk_T4S5 = unfactor(as.factor(data.frame(T4S5 %>% filter(V3=="subjects", V2==2, V4==15))[c(1:6),2589]))
Risk_T4S6 = unfactor(as.factor(data.frame(T4S6 %>% filter(V3=="subjects", V2==2, V4==15))[c(1:6),2589]))

Risk_agg = c()

for (t in c(1,3,4)){
for (s in 1:6){
session_num=s
treatment_num=t
mydata <- get(paste("Risk_T",t,paste("S",s,sep=""),sep=""))
mydata = t(t(as.data.frame(mydata)))
session = as.data.frame(rep(session_num,6))
treatment = as.data.frame(rep(treatment_num,6))
player = as.data.frame(c(1:6))

mydata = cbind(player,mydata)
mydata = cbind(session,mydata)
mydata = cbind(treatment,mydata)

Risk_agg = rbind(Risk_agg,mydata)
}}
colnames(Risk_agg) = c("Treatment","S","P","Risk")

ggplot(Risk_agg, aes(x=Risk)) + 
  geom_histogram(fill="pink", color="grey50", binwidth=0.5)+
  ggtitle("Risk Distribution (Extreme risk seeking = 1)") + 
  scale_x_continuous(name = "Risk", breaks = seq(0, 10, by = 1)) + 
  scale_y_continuous(name = "Count", breaks = seq(0, 100, by = 5))


```

## Control Treatment

```{r, echo= FALSE, message=FALSE,warning = FALSE}
mydata = data.frame(Risk_agg %>% filter(Treatment==1,S==1))
S1 = ggplot(mydata, aes(x=Risk)) + 
  geom_histogram(fill="pink", color="grey50", binwidth=0.5)+
  ggtitle("Session 1") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0.5,7.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6)) +
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(Risk_agg %>% filter(Treatment==1,S==2))
S2 = ggplot(mydata, aes(x=Risk)) + 
  geom_histogram(fill="pink", color="grey50", binwidth=0.5)+
  ggtitle("Session 2") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0.5,7.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(Risk_agg %>% filter(Treatment==1,S==3))
S3 = ggplot(mydata, aes(x=Risk)) + 
  geom_histogram(fill="pink", color="grey50", binwidth=0.5)+
  ggtitle("Session 3") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0.5,7.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(Risk_agg %>% filter(Treatment==1,S==4))
S4 = ggplot(mydata, aes(x=Risk)) + 
  geom_histogram(fill="pink", color="grey50", binwidth=0.5)+
  ggtitle("Session 4") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0.5,7.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(Risk_agg %>% filter(Treatment==1,S==5))
S5 = ggplot(mydata, aes(x=Risk)) + 
  geom_histogram(fill="pink", color="grey50", binwidth=0.5)+
  ggtitle("Session 5") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0.5,7.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(Risk_agg %>% filter(Treatment==1,S==6))
S6 = ggplot(mydata, aes(x=Risk)) + 
  geom_histogram(fill="pink", color="grey50", binwidth=0.5)+
  ggtitle("Session 6") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0.5,7.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6))+
  rremove("ylab")+ rremove("xlab")

ggarrange(S1, S2, S3, S4, S5, S6,
                    ncol = 2, nrow = 3)
```


## Treatment 3

```{r, echo= FALSE, message=FALSE,warning = FALSE}
mydata = data.frame(Risk_agg %>% filter(Treatment==3,S==1))
S1 = ggplot(mydata, aes(x=Risk)) + 
  geom_histogram(fill="pink", color="grey50", binwidth=0.5)+
  ggtitle("Session 1") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0.5,7.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6)) +
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(Risk_agg %>% filter(Treatment==3,S==2))
S2 = ggplot(mydata, aes(x=Risk)) + 
  geom_histogram(fill="pink", color="grey50", binwidth=0.5)+
  ggtitle("Session 2") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0.5,7.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(Risk_agg %>% filter(Treatment==3,S==3))
S3 = ggplot(mydata, aes(x=Risk)) + 
  geom_histogram(fill="pink", color="grey50", binwidth=0.5)+
  ggtitle("Session 3") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0.5,7.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(Risk_agg %>% filter(Treatment==3,S==4))
S4 = ggplot(mydata, aes(x=Risk)) + 
  geom_histogram(fill="pink", color="grey50", binwidth=0.5)+
  ggtitle("Session 4") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0.5,7.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(Risk_agg %>% filter(Treatment==3,S==5))
S5 = ggplot(mydata, aes(x=Risk)) + 
  geom_histogram(fill="pink", color="grey50", binwidth=0.5)+
  ggtitle("Session 5") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0.5,7.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(Risk_agg %>% filter(Treatment==3,S==6))
S6 = ggplot(mydata, aes(x=Risk)) + 
  geom_histogram(fill="pink", color="grey50", binwidth=0.5)+
  ggtitle("Session 6") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0.5,7.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6))+
  rremove("ylab")+ rremove("xlab")

ggarrange(S1, S2, S3, S4, S5, S6,
                    ncol = 2, nrow = 3)
```


## Treatment 4

```{r, echo= FALSE, message=FALSE,warning = FALSE}
mydata = data.frame(Risk_agg %>% filter(Treatment==4,S==1))
S1 = ggplot(mydata, aes(x=Risk)) + 
  geom_histogram(fill="pink", color="grey50", binwidth=0.5)+
  ggtitle("Session 1") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0.5,7.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6)) +
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(Risk_agg %>% filter(Treatment==4,S==2))
S2 = ggplot(mydata, aes(x=Risk)) + 
  geom_histogram(fill="pink", color="grey50", binwidth=0.5)+
  ggtitle("Session 2") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0.5,7.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(Risk_agg %>% filter(Treatment==4,S==3))
S3 = ggplot(mydata, aes(x=Risk)) + 
  geom_histogram(fill="pink", color="grey50", binwidth=0.5)+
  ggtitle("Session 3") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0.5,7.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(Risk_agg %>% filter(Treatment==4,S==4))
S4 = ggplot(mydata, aes(x=Risk)) + 
  geom_histogram(fill="pink", color="grey50", binwidth=0.5)+
  ggtitle("Session 4") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0.5,7.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(Risk_agg %>% filter(Treatment==4,S==5))
S5 = ggplot(mydata, aes(x=Risk)) + 
  geom_histogram(fill="pink", color="grey50", binwidth=0.5)+
  ggtitle("Session 5") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0.5,7.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6))+
  rremove("ylab")+ rremove("xlab")

mydata = data.frame(Risk_agg %>% filter(Treatment==4,S==6))
S6 = ggplot(mydata, aes(x=Risk)) + 
  geom_histogram(fill="pink", color="grey50", binwidth=0.5)+
  ggtitle("Session 6") + 
  scale_x_continuous(name = "", breaks = seq(0, 10, by = 1),limits =c(0.5,7.5)) + 
  scale_y_continuous(name = "", breaks = seq(0, 35, by = 1),limits =c(0,6))+
  rremove("ylab")+ rremove("xlab")

ggarrange(S1, S2, S3, S4, S5, S6,
                    ncol = 2, nrow = 3)
```


# Beliefs vs Inform to Others (per sucject)

```{r, echo= FALSE, message=FALSE,warning = FALSE}
### beliefs
T3S1P1_B = unfactor(as.factor(data.frame(T3S1 %>% filter(V3=="subjects", V2==2,V5==1,))[c(1:15),15]))
T3S1P2_B = unfactor(as.factor(data.frame(T3S1 %>% filter(V3=="subjects", V2==2,V5==2,))[c(1:15),15]))
T3S1P3_B = unfactor(as.factor(data.frame(T3S1 %>% filter(V3=="subjects", V2==2,V5==3,))[c(1:15),15]))
T3S1P4_B = unfactor(as.factor(data.frame(T3S1 %>% filter(V3=="subjects", V2==2,V5==4,))[c(1:15),15]))
T3S1P5_B = unfactor(as.factor(data.frame(T3S1 %>% filter(V3=="subjects", V2==2,V5==5,))[c(1:15),15]))
T3S1P6_B = unfactor(as.factor(data.frame(T3S1 %>% filter(V3=="subjects", V2==2,V5==6,))[c(1:15),15]))

T4S1P1_B = unfactor(as.factor(data.frame(T4S1 %>% filter(V3=="subjects", V2==2,V5==1,))[c(1:15),15]))
T4S1P2_B = unfactor(as.factor(data.frame(T4S1 %>% filter(V3=="subjects", V2==2,V5==2,))[c(1:15),15]))
T4S1P3_B = unfactor(as.factor(data.frame(T4S1 %>% filter(V3=="subjects", V2==2,V5==3,))[c(1:15),15]))
T4S1P4_B = unfactor(as.factor(data.frame(T4S1 %>% filter(V3=="subjects", V2==2,V5==4,))[c(1:15),15]))
T4S1P5_B = unfactor(as.factor(data.frame(T4S1 %>% filter(V3=="subjects", V2==2,V5==5,))[c(1:15),15]))
T4S1P6_B = unfactor(as.factor(data.frame(T4S1 %>% filter(V3=="subjects", V2==2,V5==6,))[c(1:15),15]))

T3S2P1_B = unfactor(as.factor(data.frame(T3S2 %>% filter(V3=="subjects", V2==2,V5==1,))[c(1:15),15]))
T3S2P2_B = unfactor(as.factor(data.frame(T3S2 %>% filter(V3=="subjects", V2==2,V5==2,))[c(1:15),15]))
T3S2P3_B = unfactor(as.factor(data.frame(T3S2 %>% filter(V3=="subjects", V2==2,V5==3,))[c(1:15),15]))
T3S2P4_B = unfactor(as.factor(data.frame(T3S2 %>% filter(V3=="subjects", V2==2,V5==4,))[c(1:15),15]))
T3S2P5_B = unfactor(as.factor(data.frame(T3S2 %>% filter(V3=="subjects", V2==2,V5==5,))[c(1:15),15]))
T3S2P6_B = unfactor(as.factor(data.frame(T3S2 %>% filter(V3=="subjects", V2==2,V5==6,))[c(1:15),15]))

T4S2P1_B = unfactor(as.factor(data.frame(T4S2 %>% filter(V3=="subjects", V2==2,V5==1,))[c(1:15),15]))
T4S2P2_B = unfactor(as.factor(data.frame(T4S2 %>% filter(V3=="subjects", V2==2,V5==2,))[c(1:15),15]))
T4S2P3_B = unfactor(as.factor(data.frame(T4S2 %>% filter(V3=="subjects", V2==2,V5==3,))[c(1:15),15]))
T4S2P4_B = unfactor(as.factor(data.frame(T4S2 %>% filter(V3=="subjects", V2==2,V5==4,))[c(1:15),15]))
T4S2P5_B = unfactor(as.factor(data.frame(T4S2 %>% filter(V3=="subjects", V2==2,V5==5,))[c(1:15),15]))
T4S2P6_B = unfactor(as.factor(data.frame(T4S2 %>% filter(V3=="subjects", V2==2,V5==6,))[c(1:15),15]))

T3S3P1_B = unfactor(as.factor(data.frame(T3S3 %>% filter(V3=="subjects", V2==2,V5==1,))[c(1:15),15]))
T3S3P2_B = unfactor(as.factor(data.frame(T3S3 %>% filter(V3=="subjects", V2==2,V5==2,))[c(1:15),15]))
T3S3P3_B = unfactor(as.factor(data.frame(T3S3 %>% filter(V3=="subjects", V2==2,V5==3,))[c(1:15),15]))
T3S3P4_B = unfactor(as.factor(data.frame(T3S3 %>% filter(V3=="subjects", V2==2,V5==4,))[c(1:15),15]))
T3S3P5_B = unfactor(as.factor(data.frame(T3S3 %>% filter(V3=="subjects", V2==2,V5==5,))[c(1:15),15]))
T3S3P6_B = unfactor(as.factor(data.frame(T3S3 %>% filter(V3=="subjects", V2==2,V5==6,))[c(1:15),15]))

T4S3P1_B = unfactor(as.factor(data.frame(T4S3 %>% filter(V3=="subjects", V2==2,V5==1,))[c(1:15),15]))
T4S3P2_B = unfactor(as.factor(data.frame(T4S3 %>% filter(V3=="subjects", V2==2,V5==2,))[c(1:15),15]))
T4S3P3_B = unfactor(as.factor(data.frame(T4S3 %>% filter(V3=="subjects", V2==2,V5==3,))[c(1:15),15]))
T4S3P4_B = unfactor(as.factor(data.frame(T4S3 %>% filter(V3=="subjects", V2==2,V5==4,))[c(1:15),15]))
T4S3P5_B = unfactor(as.factor(data.frame(T4S3 %>% filter(V3=="subjects", V2==2,V5==5,))[c(1:15),15]))
T4S3P6_B = unfactor(as.factor(data.frame(T4S3 %>% filter(V3=="subjects", V2==2,V5==6,))[c(1:15),15]))

T3S4P1_B = unfactor(as.factor(data.frame(T3S4 %>% filter(V3=="subjects", V2==2,V5==1,))[c(1:15),15]))
T3S4P2_B = unfactor(as.factor(data.frame(T3S4 %>% filter(V3=="subjects", V2==2,V5==2,))[c(1:15),15]))
T3S4P3_B = unfactor(as.factor(data.frame(T3S4 %>% filter(V3=="subjects", V2==2,V5==3,))[c(1:15),15]))
T3S4P4_B = unfactor(as.factor(data.frame(T3S4 %>% filter(V3=="subjects", V2==2,V5==4,))[c(1:15),15]))
T3S4P5_B = unfactor(as.factor(data.frame(T3S4 %>% filter(V3=="subjects", V2==2,V5==5,))[c(1:15),15]))
T3S4P6_B = unfactor(as.factor(data.frame(T3S4 %>% filter(V3=="subjects", V2==2,V5==6,))[c(1:15),15]))

T4S4P1_B = unfactor(as.factor(data.frame(T4S4 %>% filter(V3=="subjects", V2==2,V5==1,))[c(1:15),15]))
T4S4P2_B = unfactor(as.factor(data.frame(T4S4 %>% filter(V3=="subjects", V2==2,V5==2,))[c(1:15),15]))
T4S4P3_B = unfactor(as.factor(data.frame(T4S4 %>% filter(V3=="subjects", V2==2,V5==3,))[c(1:15),15]))
T4S4P4_B = unfactor(as.factor(data.frame(T4S4 %>% filter(V3=="subjects", V2==2,V5==4,))[c(1:15),15]))
T4S4P5_B = unfactor(as.factor(data.frame(T4S4 %>% filter(V3=="subjects", V2==2,V5==5,))[c(1:15),15]))
T4S4P6_B = unfactor(as.factor(data.frame(T4S4 %>% filter(V3=="subjects", V2==2,V5==6,))[c(1:15),15]))

T3S5P1_B = unfactor(as.factor(data.frame(T3S5 %>% filter(V3=="subjects", V2==2,V5==1,))[c(1:15),15]))
T3S5P2_B = unfactor(as.factor(data.frame(T3S5 %>% filter(V3=="subjects", V2==2,V5==2,))[c(1:15),15]))
T3S5P3_B = unfactor(as.factor(data.frame(T3S5 %>% filter(V3=="subjects", V2==2,V5==3,))[c(1:15),15]))
T3S5P4_B = unfactor(as.factor(data.frame(T3S5 %>% filter(V3=="subjects", V2==2,V5==4,))[c(1:15),15]))
T3S5P5_B = unfactor(as.factor(data.frame(T3S5 %>% filter(V3=="subjects", V2==2,V5==5,))[c(1:15),15]))
T3S5P6_B = unfactor(as.factor(data.frame(T3S5 %>% filter(V3=="subjects", V2==2,V5==6,))[c(1:15),15]))

T4S5P1_B = unfactor(as.factor(data.frame(T4S5 %>% filter(V3=="subjects", V2==2,V5==1,))[c(1:15),15]))
T4S5P2_B = unfactor(as.factor(data.frame(T4S5 %>% filter(V3=="subjects", V2==2,V5==2,))[c(1:15),15]))
T4S5P3_B = unfactor(as.factor(data.frame(T4S5 %>% filter(V3=="subjects", V2==2,V5==3,))[c(1:15),15]))
T4S5P4_B = unfactor(as.factor(data.frame(T4S5 %>% filter(V3=="subjects", V2==2,V5==4,))[c(1:15),15]))
T4S5P5_B = unfactor(as.factor(data.frame(T4S5 %>% filter(V3=="subjects", V2==2,V5==5,))[c(1:15),15]))
T4S5P6_B = unfactor(as.factor(data.frame(T4S5 %>% filter(V3=="subjects", V2==2,V5==6,))[c(1:15),15]))

T3S6P1_B = unfactor(as.factor(data.frame(T3S6 %>% filter(V3=="subjects", V2==2,V5==1,))[c(1:15),15]))
T3S6P2_B = unfactor(as.factor(data.frame(T3S6 %>% filter(V3=="subjects", V2==2,V5==2,))[c(1:15),15]))
T3S6P3_B = unfactor(as.factor(data.frame(T3S6 %>% filter(V3=="subjects", V2==2,V5==3,))[c(1:15),15]))
T3S6P4_B = unfactor(as.factor(data.frame(T3S6 %>% filter(V3=="subjects", V2==2,V5==4,))[c(1:15),15]))
T3S6P5_B = unfactor(as.factor(data.frame(T3S6 %>% filter(V3=="subjects", V2==2,V5==5,))[c(1:15),15]))
T3S6P6_B = unfactor(as.factor(data.frame(T3S6 %>% filter(V3=="subjects", V2==2,V5==6,))[c(1:15),15]))

T4S6P1_B = unfactor(as.factor(data.frame(T4S6 %>% filter(V3=="subjects", V2==2,V5==1,))[c(1:15),15]))
T4S6P2_B = unfactor(as.factor(data.frame(T4S6 %>% filter(V3=="subjects", V2==2,V5==2,))[c(1:15),15]))
T4S6P3_B = unfactor(as.factor(data.frame(T4S6 %>% filter(V3=="subjects", V2==2,V5==3,))[c(1:15),15]))
T4S6P4_B = unfactor(as.factor(data.frame(T4S6 %>% filter(V3=="subjects", V2==2,V5==4,))[c(1:15),15]))
T4S6P5_B = unfactor(as.factor(data.frame(T4S6 %>% filter(V3=="subjects", V2==2,V5==5,))[c(1:15),15]))
T4S6P6_B = unfactor(as.factor(data.frame(T4S6 %>% filter(V3=="subjects", V2==2,V5==6,))[c(1:15),15]))

###inform
T3S1P1_i = unfactor(as.factor(data.frame(T3S1 %>% filter(V3=="subjects", V2==2,V5==1,))[c(1:15),14]))
T3S1P2_i = unfactor(as.factor(data.frame(T3S1 %>% filter(V3=="subjects", V2==2,V5==2,))[c(1:15),14]))
T3S1P3_i = unfactor(as.factor(data.frame(T3S1 %>% filter(V3=="subjects", V2==2,V5==3,))[c(1:15),14]))
T3S1P4_i = unfactor(as.factor(data.frame(T3S1 %>% filter(V3=="subjects", V2==2,V5==4,))[c(1:15),14]))
T3S1P5_i = unfactor(as.factor(data.frame(T3S1 %>% filter(V3=="subjects", V2==2,V5==5,))[c(1:15),14]))
T3S1P6_i = unfactor(as.factor(data.frame(T3S1 %>% filter(V3=="subjects", V2==2,V5==6,))[c(1:15),14]))

T4S1P1_i = unfactor(as.factor(data.frame(T4S1 %>% filter(V3=="subjects", V2==2,V5==1,))[c(1:15),14]))
T4S1P2_i = unfactor(as.factor(data.frame(T4S1 %>% filter(V3=="subjects", V2==2,V5==2,))[c(1:15),14]))
T4S1P3_i = unfactor(as.factor(data.frame(T4S1 %>% filter(V3=="subjects", V2==2,V5==3,))[c(1:15),14]))
T4S1P4_i = unfactor(as.factor(data.frame(T4S1 %>% filter(V3=="subjects", V2==2,V5==4,))[c(1:15),14]))
T4S1P5_i = unfactor(as.factor(data.frame(T4S1 %>% filter(V3=="subjects", V2==2,V5==5,))[c(1:15),14]))
T4S1P6_i = unfactor(as.factor(data.frame(T4S1 %>% filter(V3=="subjects", V2==2,V5==6,))[c(1:15),14]))

T3S2P1_i = unfactor(as.factor(data.frame(T3S2 %>% filter(V3=="subjects", V2==2,V5==1,))[c(1:15),14]))
T3S2P2_i = unfactor(as.factor(data.frame(T3S2 %>% filter(V3=="subjects", V2==2,V5==2,))[c(1:15),14]))
T3S2P3_i = unfactor(as.factor(data.frame(T3S2 %>% filter(V3=="subjects", V2==2,V5==3,))[c(1:15),14]))
T3S2P4_i = unfactor(as.factor(data.frame(T3S2 %>% filter(V3=="subjects", V2==2,V5==4,))[c(1:15),14]))
T3S2P5_i = unfactor(as.factor(data.frame(T3S2 %>% filter(V3=="subjects", V2==2,V5==5,))[c(1:15),14]))
T3S2P6_i = unfactor(as.factor(data.frame(T3S2 %>% filter(V3=="subjects", V2==2,V5==6,))[c(1:15),14]))

T4S2P1_i = unfactor(as.factor(data.frame(T4S2 %>% filter(V3=="subjects", V2==2,V5==1,))[c(1:15),14]))
T4S2P2_i = unfactor(as.factor(data.frame(T4S2 %>% filter(V3=="subjects", V2==2,V5==2,))[c(1:15),14]))
T4S2P3_i = unfactor(as.factor(data.frame(T4S2 %>% filter(V3=="subjects", V2==2,V5==3,))[c(1:15),14]))
T4S2P4_i = unfactor(as.factor(data.frame(T4S2 %>% filter(V3=="subjects", V2==2,V5==4,))[c(1:15),14]))
T4S2P5_i = unfactor(as.factor(data.frame(T4S2 %>% filter(V3=="subjects", V2==2,V5==5,))[c(1:15),14]))
T4S2P6_i = unfactor(as.factor(data.frame(T4S2 %>% filter(V3=="subjects", V2==2,V5==6,))[c(1:15),14]))

T3S3P1_i = unfactor(as.factor(data.frame(T3S3 %>% filter(V3=="subjects", V2==2,V5==1,))[c(1:15),14]))
T3S3P2_i = unfactor(as.factor(data.frame(T3S3 %>% filter(V3=="subjects", V2==2,V5==2,))[c(1:15),14]))
T3S3P3_i = unfactor(as.factor(data.frame(T3S3 %>% filter(V3=="subjects", V2==2,V5==3,))[c(1:15),14]))
T3S3P4_i = unfactor(as.factor(data.frame(T3S3 %>% filter(V3=="subjects", V2==2,V5==4,))[c(1:15),14]))
T3S3P5_i = unfactor(as.factor(data.frame(T3S3 %>% filter(V3=="subjects", V2==2,V5==5,))[c(1:15),14]))
T3S3P6_i = unfactor(as.factor(data.frame(T3S3 %>% filter(V3=="subjects", V2==2,V5==6,))[c(1:15),14]))

T4S3P1_i = unfactor(as.factor(data.frame(T4S3 %>% filter(V3=="subjects", V2==2,V5==1,))[c(1:15),14]))
T4S3P2_i = unfactor(as.factor(data.frame(T4S3 %>% filter(V3=="subjects", V2==2,V5==2,))[c(1:15),14]))
T4S3P3_i = unfactor(as.factor(data.frame(T4S3 %>% filter(V3=="subjects", V2==2,V5==3,))[c(1:15),14]))
T4S3P4_i = unfactor(as.factor(data.frame(T4S3 %>% filter(V3=="subjects", V2==2,V5==4,))[c(1:15),14]))
T4S3P5_i = unfactor(as.factor(data.frame(T4S3 %>% filter(V3=="subjects", V2==2,V5==5,))[c(1:15),14]))
T4S3P6_i = unfactor(as.factor(data.frame(T4S3 %>% filter(V3=="subjects", V2==2,V5==6,))[c(1:15),14]))

T3S4P1_i = unfactor(as.factor(data.frame(T3S4 %>% filter(V3=="subjects", V2==2,V5==1,))[c(1:15),14]))
T3S4P2_i = unfactor(as.factor(data.frame(T3S4 %>% filter(V3=="subjects", V2==2,V5==2,))[c(1:15),14]))
T3S4P3_i = unfactor(as.factor(data.frame(T3S4 %>% filter(V3=="subjects", V2==2,V5==3,))[c(1:15),14]))
T3S4P4_i = unfactor(as.factor(data.frame(T3S4 %>% filter(V3=="subjects", V2==2,V5==4,))[c(1:15),14]))
T3S4P5_i = unfactor(as.factor(data.frame(T3S4 %>% filter(V3=="subjects", V2==2,V5==5,))[c(1:15),14]))
T3S4P6_i = unfactor(as.factor(data.frame(T3S4 %>% filter(V3=="subjects", V2==2,V5==6,))[c(1:15),14]))

T4S4P1_i = unfactor(as.factor(data.frame(T4S4 %>% filter(V3=="subjects", V2==2,V5==1,))[c(1:15),14]))
T4S4P2_i = unfactor(as.factor(data.frame(T4S4 %>% filter(V3=="subjects", V2==2,V5==2,))[c(1:15),14]))
T4S4P3_i = unfactor(as.factor(data.frame(T4S4 %>% filter(V3=="subjects", V2==2,V5==3,))[c(1:15),14]))
T4S4P4_i = unfactor(as.factor(data.frame(T4S4 %>% filter(V3=="subjects", V2==2,V5==4,))[c(1:15),14]))
T4S4P5_i = unfactor(as.factor(data.frame(T4S4 %>% filter(V3=="subjects", V2==2,V5==5,))[c(1:15),14]))
T4S4P6_i = unfactor(as.factor(data.frame(T4S4 %>% filter(V3=="subjects", V2==2,V5==6,))[c(1:15),14]))

T3S5P1_i = unfactor(as.factor(data.frame(T3S5 %>% filter(V3=="subjects", V2==2,V5==1,))[c(1:15),14]))
T3S5P2_i = unfactor(as.factor(data.frame(T3S5 %>% filter(V3=="subjects", V2==2,V5==2,))[c(1:15),14]))
T3S5P3_i = unfactor(as.factor(data.frame(T3S5 %>% filter(V3=="subjects", V2==2,V5==3,))[c(1:15),14]))
T3S5P4_i = unfactor(as.factor(data.frame(T3S5 %>% filter(V3=="subjects", V2==2,V5==4,))[c(1:15),14]))
T3S5P5_i = unfactor(as.factor(data.frame(T3S5 %>% filter(V3=="subjects", V2==2,V5==5,))[c(1:15),14]))
T3S5P6_i = unfactor(as.factor(data.frame(T3S5 %>% filter(V3=="subjects", V2==2,V5==6,))[c(1:15),14]))

T4S5P1_i = unfactor(as.factor(data.frame(T4S5 %>% filter(V3=="subjects", V2==2,V5==1,))[c(1:15),14]))
T4S5P2_i = unfactor(as.factor(data.frame(T4S5 %>% filter(V3=="subjects", V2==2,V5==2,))[c(1:15),14]))
T4S5P3_i = unfactor(as.factor(data.frame(T4S5 %>% filter(V3=="subjects", V2==2,V5==3,))[c(1:15),14]))
T4S5P4_i = unfactor(as.factor(data.frame(T4S5 %>% filter(V3=="subjects", V2==2,V5==4,))[c(1:15),14]))
T4S5P5_i = unfactor(as.factor(data.frame(T4S5 %>% filter(V3=="subjects", V2==2,V5==5,))[c(1:15),14]))
T4S5P6_i = unfactor(as.factor(data.frame(T4S5 %>% filter(V3=="subjects", V2==2,V5==6,))[c(1:15),14]))

T3S6P1_i = unfactor(as.factor(data.frame(T3S6 %>% filter(V3=="subjects", V2==2,V5==1,))[c(1:15),14]))
T3S6P2_i = unfactor(as.factor(data.frame(T3S6 %>% filter(V3=="subjects", V2==2,V5==2,))[c(1:15),14]))
T3S6P3_i = unfactor(as.factor(data.frame(T3S6 %>% filter(V3=="subjects", V2==2,V5==3,))[c(1:15),14]))
T3S6P4_i = unfactor(as.factor(data.frame(T3S6 %>% filter(V3=="subjects", V2==2,V5==4,))[c(1:15),14]))
T3S6P5_i = unfactor(as.factor(data.frame(T3S6 %>% filter(V3=="subjects", V2==2,V5==5,))[c(1:15),14]))
T3S6P6_i = unfactor(as.factor(data.frame(T3S6 %>% filter(V3=="subjects", V2==2,V5==6,))[c(1:15),14]))

T4S6P1_i = unfactor(as.factor(data.frame(T4S6 %>% filter(V3=="subjects", V2==2,V5==1,))[c(1:15),14]))
T4S6P2_i = unfactor(as.factor(data.frame(T4S6 %>% filter(V3=="subjects", V2==2,V5==2,))[c(1:15),14]))
T4S6P3_i = unfactor(as.factor(data.frame(T4S6 %>% filter(V3=="subjects", V2==2,V5==3,))[c(1:15),14]))
T4S6P4_i = unfactor(as.factor(data.frame(T4S6 %>% filter(V3=="subjects", V2==2,V5==4,))[c(1:15),14]))
T4S6P5_i = unfactor(as.factor(data.frame(T4S6 %>% filter(V3=="subjects", V2==2,V5==5,))[c(1:15),14]))
T4S6P6_i = unfactor(as.factor(data.frame(T4S6 %>% filter(V3=="subjects", V2==2,V5==6,))[c(1:15),14]))

subjects_b_i = c()

for (t in 3:4){
  for (s in 1:6){
    for (p in 1:6){
      
    mydata = get(paste("T",t,"S",s,"P",p,"_B",sep=""))
    subjects_b_i = as.data.frame(cbind(subjects_b_i,mydata))
    names(subjects_b_i)[length(names(subjects_b_i))]<-paste("T",t,"S",s,"P",p,"_B",sep="")
    } 
    }
}
for (t in 3:4){
  for (s in 1:6){
    for (p in 1:6){
      
    mydata = get(paste("T",t,"S",s,"P",p,"_i",sep=""))
    subjects_b_i = as.data.frame(cbind(subjects_b_i,mydata))
    names(subjects_b_i)[length(names(subjects_b_i))]<-paste("T",t,"S",s,"P",p,"_i",sep="")
    } 
    }
}
period = c(1:15)

```


## Treatment 3 {.tabset}

### Session 1

```{r, echo= FALSE, message=FALSE, warning=FALSE, fig.width=9, fig.height=9}

P1 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T3S1P1_B, color = "Belief"))+ geom_point(aes(y = T3S1P1_B, color = "Belief")) + 
  geom_line(aes(y = T3S1P1_i, color = "Inform")) + geom_point(aes(y = T3S1P1_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 1")

P2 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T3S1P2_B, color = "Belief"))+ geom_point(aes(y = T3S1P2_B, color = "Belief")) + 
  geom_line(aes(y = T3S1P2_i, color = "Inform")) + geom_point(aes(y = T3S1P2_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 2")

P3 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T3S1P3_B, color = "Belief"))+ geom_point(aes(y = T3S1P3_B, color = "Belief")) + 
  geom_line(aes(y = T3S1P3_i, color = "Inform")) + geom_point(aes(y = T3S1P3_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 3")

P4 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T3S1P4_B, color = "Belief"))+ geom_point(aes(y = T3S1P4_B, color = "Belief")) + 
  geom_line(aes(y = T3S1P4_i, color = "Inform")) + geom_point(aes(y = T3S1P4_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 4")

P5 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T3S1P5_B, color = "Belief"))+ geom_point(aes(y = T3S1P5_B, color = "Belief")) + 
  geom_line(aes(y = T3S1P5_i, color = "Inform")) + geom_point(aes(y = T3S1P5_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 5")

P6 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T3S1P6_B, color = "Belief"))+ geom_point(aes(y = T3S1P6_B, color = "Belief")) + 
  geom_line(aes(y = T3S1P6_i, color = "Inform")) + geom_point(aes(y = T3S1P6_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 6")

ggarrange(P1, P2,P3,P4,P5,P6,
                    ncol = 2, nrow = 3, legend = "top",common.legend = TRUE)
```





### Session 2

```{r, echo= FALSE, message=FALSE, warning=FALSE, fig.width=9, fig.height=9}

P1 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T3S2P1_B, color = "Belief"))+ geom_point(aes(y = T3S2P1_B, color = "Belief")) + 
  geom_line(aes(y = T3S2P1_i, color = "Inform")) + geom_point(aes(y = T3S2P1_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 1")

P2 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T3S2P2_B, color = "Belief"))+ geom_point(aes(y = T3S2P2_B, color = "Belief")) + 
  geom_line(aes(y = T3S2P2_i, color = "Inform")) + geom_point(aes(y = T3S2P2_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 2")

P3 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T3S2P3_B, color = "Belief"))+ geom_point(aes(y = T3S2P3_B, color = "Belief")) + 
  geom_line(aes(y = T3S2P3_i, color = "Inform")) + geom_point(aes(y = T3S2P3_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 3")

P4 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T3S2P4_B, color = "Belief"))+ geom_point(aes(y = T3S2P4_B, color = "Belief")) + 
  geom_line(aes(y = T3S2P4_i, color = "Inform")) + geom_point(aes(y = T3S2P4_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 4")

P5 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T3S2P5_B, color = "Belief"))+ geom_point(aes(y = T3S2P5_B, color = "Belief")) + 
  geom_line(aes(y = T3S2P5_i, color = "Inform")) + geom_point(aes(y = T3S2P5_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 5")

P6 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T3S2P6_B, color = "Belief"))+ geom_point(aes(y = T3S2P6_B, color = "Belief")) + 
  geom_line(aes(y = T3S2P6_i, color = "Inform")) + geom_point(aes(y = T3S2P6_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 6")

ggarrange(P1, P2,P3,P4,P5,P6,
                    ncol = 2, nrow = 3, legend = "top",common.legend = TRUE)
```

### Session 3

```{r, echo= FALSE, message=FALSE, warning=FALSE, fig.width=9, fig.height=9}

P1 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T3S3P1_B, color = "Belief"))+ geom_point(aes(y = T3S3P1_B, color = "Belief")) + 
  geom_line(aes(y = T3S3P1_i, color = "Inform")) + geom_point(aes(y = T3S3P1_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 1")

P2 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T3S3P2_B, color = "Belief"))+ geom_point(aes(y = T3S3P2_B, color = "Belief")) + 
  geom_line(aes(y = T3S3P2_i, color = "Inform")) + geom_point(aes(y = T3S3P2_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 2")

P3 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T3S3P3_B, color = "Belief"))+ geom_point(aes(y = T3S3P3_B, color = "Belief")) + 
  geom_line(aes(y = T3S3P3_i, color = "Inform")) + geom_point(aes(y = T3S3P3_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 3")

P4 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T3S3P4_B, color = "Belief"))+ geom_point(aes(y = T3S3P4_B, color = "Belief")) + 
  geom_line(aes(y = T3S3P4_i, color = "Inform")) + geom_point(aes(y = T3S3P4_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 4")

P5 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T3S3P5_B, color = "Belief"))+ geom_point(aes(y = T3S3P5_B, color = "Belief")) + 
  geom_line(aes(y = T3S3P5_i, color = "Inform")) + geom_point(aes(y = T3S3P5_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 5")

P6 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T3S3P6_B, color = "Belief"))+ geom_point(aes(y = T3S3P6_B, color = "Belief")) + 
  geom_line(aes(y = T3S3P6_i, color = "Inform")) + geom_point(aes(y = T3S3P6_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 6")

ggarrange(P1, P2,P3,P4,P5,P6,
                    ncol = 2, nrow = 3, legend = "top",common.legend = TRUE)
```


### Session 4

```{r, echo= FALSE, message=FALSE, warning=FALSE, fig.width=9, fig.height=9}

P1 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T3S4P1_B, color = "Belief"))+ geom_point(aes(y = T3S4P1_B, color = "Belief")) + 
  geom_line(aes(y = T3S4P1_i, color = "Inform")) + geom_point(aes(y = T3S4P1_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 1")

P2 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T3S4P2_B, color = "Belief"))+ geom_point(aes(y = T3S4P2_B, color = "Belief")) + 
  geom_line(aes(y = T3S4P2_i, color = "Inform")) + geom_point(aes(y = T3S4P2_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 2")

P3 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T3S4P3_B, color = "Belief"))+ geom_point(aes(y = T3S4P3_B, color = "Belief")) + 
  geom_line(aes(y = T3S4P3_i, color = "Inform")) + geom_point(aes(y = T3S4P3_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 3")

P4 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T3S4P4_B, color = "Belief"))+ geom_point(aes(y = T3S4P4_B, color = "Belief")) + 
  geom_line(aes(y = T3S4P4_i, color = "Inform")) + geom_point(aes(y = T3S4P4_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 4")

P5 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T3S4P5_B, color = "Belief"))+ geom_point(aes(y = T3S4P5_B, color = "Belief")) + 
  geom_line(aes(y = T3S4P5_i, color = "Inform")) + geom_point(aes(y = T3S4P5_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 5")

P6 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T3S4P6_B, color = "Belief"))+ geom_point(aes(y = T3S4P6_B, color = "Belief")) + 
  geom_line(aes(y = T3S4P6_i, color = "Inform")) + geom_point(aes(y = T3S4P6_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 6")

ggarrange(P1, P2,P3,P4,P5,P6,
                    ncol = 2, nrow = 3, legend = "top",common.legend = TRUE)
```


### Session 5

```{r, echo= FALSE, message=FALSE, warning=FALSE, fig.width=9, fig.height=9}

P1 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T3S5P1_B, color = "Belief"))+ geom_point(aes(y = T3S5P1_B, color = "Belief")) + 
  geom_line(aes(y = T3S5P1_i, color = "Inform")) + geom_point(aes(y = T3S5P1_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 1")

P2 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T3S5P2_B, color = "Belief"))+ geom_point(aes(y = T3S5P2_B, color = "Belief")) + 
  geom_line(aes(y = T3S5P2_i, color = "Inform")) + geom_point(aes(y = T3S5P2_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 2")

P3 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T3S5P3_B, color = "Belief"))+ geom_point(aes(y = T3S5P3_B, color = "Belief")) + 
  geom_line(aes(y = T3S5P3_i, color = "Inform")) + geom_point(aes(y = T3S5P3_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 3")

P4 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T3S5P4_B, color = "Belief"))+ geom_point(aes(y = T3S5P4_B, color = "Belief")) + 
  geom_line(aes(y = T3S5P4_i, color = "Inform")) + geom_point(aes(y = T3S5P4_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 4")

P5 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T3S5P5_B, color = "Belief"))+ geom_point(aes(y = T3S5P5_B, color = "Belief")) + 
  geom_line(aes(y = T3S5P5_i, color = "Inform")) + geom_point(aes(y = T3S5P5_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 5")

P6 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T3S5P6_B, color = "Belief"))+ geom_point(aes(y = T3S5P6_B, color = "Belief")) + 
  geom_line(aes(y = T3S5P6_i, color = "Inform")) + geom_point(aes(y = T3S5P6_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 6")

ggarrange(P1, P2,P3,P4,P5,P6,
                    ncol = 2, nrow = 3, legend = "top",common.legend = TRUE)
```

### Session 6

```{r, echo= FALSE, message=FALSE, warning=FALSE, fig.width=9, fig.height=9}

P1 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T3S6P1_B, color = "Belief"))+ geom_point(aes(y = T3S6P1_B, color = "Belief")) + 
  geom_line(aes(y = T3S6P1_i, color = "Inform")) + geom_point(aes(y = T3S6P1_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 1")

P2 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T3S6P2_B, color = "Belief"))+ geom_point(aes(y = T3S6P2_B, color = "Belief")) + 
  geom_line(aes(y = T3S6P2_i, color = "Inform")) + geom_point(aes(y = T3S6P2_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 2")

P3 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T3S6P3_B, color = "Belief"))+ geom_point(aes(y = T3S6P3_B, color = "Belief")) + 
  geom_line(aes(y = T3S6P3_i, color = "Inform")) + geom_point(aes(y = T3S6P3_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 3")

P4 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T3S6P4_B, color = "Belief"))+ geom_point(aes(y = T3S6P4_B, color = "Belief")) + 
  geom_line(aes(y = T3S6P4_i, color = "Inform")) + geom_point(aes(y = T3S6P4_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 4")

P5 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T3S6P5_B, color = "Belief"))+ geom_point(aes(y = T3S6P5_B, color = "Belief")) + 
  geom_line(aes(y = T3S6P5_i, color = "Inform")) + geom_point(aes(y = T3S6P5_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 5")

P6 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T3S6P6_B, color = "Belief"))+ geom_point(aes(y = T3S6P6_B, color = "Belief")) + 
  geom_line(aes(y = T3S6P6_i, color = "Inform")) + geom_point(aes(y = T3S6P6_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 6")

ggarrange(P1, P2,P3,P4,P5,P6,
                    ncol = 2, nrow = 3, legend = "top",common.legend = TRUE)
```






## Treatment 4 {.tabset}

### Session 1

```{r, echo= FALSE, message=FALSE, warning=FALSE, fig.width=9, fig.height=9}

P1 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T4S1P1_B, color = "Belief"))+ geom_point(aes(y = T4S1P1_B, color = "Belief")) + 
  geom_line(aes(y = T4S1P1_i, color = "Inform")) + geom_point(aes(y = T4S1P1_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 1")

P2 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T4S1P2_B, color = "Belief"))+ geom_point(aes(y = T4S1P2_B, color = "Belief")) + 
  geom_line(aes(y = T4S1P2_i, color = "Inform")) + geom_point(aes(y = T4S1P2_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 2")

P3 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T4S1P3_B, color = "Belief"))+ geom_point(aes(y = T4S1P3_B, color = "Belief")) + 
  geom_line(aes(y = T4S1P3_i, color = "Inform")) + geom_point(aes(y = T4S1P3_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 3")

P4 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T4S1P4_B, color = "Belief"))+ geom_point(aes(y = T4S1P4_B, color = "Belief")) + 
  geom_line(aes(y = T4S1P4_i, color = "Inform")) + geom_point(aes(y = T4S1P4_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 4")

P5 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T4S1P5_B, color = "Belief"))+ geom_point(aes(y = T4S1P5_B, color = "Belief")) + 
  geom_line(aes(y = T4S1P5_i, color = "Inform")) + geom_point(aes(y = T4S1P5_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 5")

P6 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T4S1P6_B, color = "Belief"))+ geom_point(aes(y = T4S1P6_B, color = "Belief")) + 
  geom_line(aes(y = T4S1P6_i, color = "Inform")) + geom_point(aes(y = T4S1P6_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 6")

ggarrange(P1, P2,P3,P4,P5,P6,
                    ncol = 2, nrow = 3, legend = "top",common.legend = TRUE)
```





### Session 2

```{r, echo= FALSE, message=FALSE, warning=FALSE, fig.width=9, fig.height=9}

P1 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T4S2P1_B, color = "Belief"))+ geom_point(aes(y = T4S2P1_B, color = "Belief")) + 
  geom_line(aes(y = T4S2P1_i, color = "Inform")) + geom_point(aes(y = T4S2P1_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 1")

P2 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T4S2P2_B, color = "Belief"))+ geom_point(aes(y = T4S2P2_B, color = "Belief")) + 
  geom_line(aes(y = T4S2P2_i, color = "Inform")) + geom_point(aes(y = T4S2P2_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 2")

P3 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T4S2P3_B, color = "Belief"))+ geom_point(aes(y = T4S2P3_B, color = "Belief")) + 
  geom_line(aes(y = T4S2P3_i, color = "Inform")) + geom_point(aes(y = T4S2P3_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 3")

P4 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T4S2P4_B, color = "Belief"))+ geom_point(aes(y = T4S2P4_B, color = "Belief")) + 
  geom_line(aes(y = T4S2P4_i, color = "Inform")) + geom_point(aes(y = T4S2P4_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 4")

P5 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T4S2P5_B, color = "Belief"))+ geom_point(aes(y = T4S2P5_B, color = "Belief")) + 
  geom_line(aes(y = T4S2P5_i, color = "Inform")) + geom_point(aes(y = T4S2P5_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 5")

P6 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T4S2P6_B, color = "Belief"))+ geom_point(aes(y = T4S2P6_B, color = "Belief")) + 
  geom_line(aes(y = T4S2P6_i, color = "Inform")) + geom_point(aes(y = T4S2P6_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 6")

ggarrange(P1, P2,P3,P4,P5,P6,
                    ncol = 2, nrow = 3, legend = "top",common.legend = TRUE)
```

### Session 3

```{r, echo= FALSE, message=FALSE, warning=FALSE, fig.width=9, fig.height=9}

P1 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T4S3P1_B, color = "Belief"))+ geom_point(aes(y = T4S3P1_B, color = "Belief")) + 
  geom_line(aes(y = T4S3P1_i, color = "Inform")) + geom_point(aes(y = T4S3P1_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 1")

P2 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T4S3P2_B, color = "Belief"))+ geom_point(aes(y = T4S3P2_B, color = "Belief")) + 
  geom_line(aes(y = T4S3P2_i, color = "Inform")) + geom_point(aes(y = T4S3P2_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 2")

P3 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T4S3P3_B, color = "Belief"))+ geom_point(aes(y = T4S3P3_B, color = "Belief")) + 
  geom_line(aes(y = T4S3P3_i, color = "Inform")) + geom_point(aes(y = T4S3P3_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 3")

P4 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T4S3P4_B, color = "Belief"))+ geom_point(aes(y = T4S3P4_B, color = "Belief")) + 
  geom_line(aes(y = T4S3P4_i, color = "Inform")) + geom_point(aes(y = T4S3P4_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 4")

P5 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T4S3P5_B, color = "Belief"))+ geom_point(aes(y = T4S3P5_B, color = "Belief")) + 
  geom_line(aes(y = T4S3P5_i, color = "Inform")) + geom_point(aes(y = T4S3P5_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 5")

P6 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T4S3P6_B, color = "Belief"))+ geom_point(aes(y = T4S3P6_B, color = "Belief")) + 
  geom_line(aes(y = T4S3P6_i, color = "Inform")) + geom_point(aes(y = T4S3P6_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 6")

ggarrange(P1, P2,P3,P4,P5,P6,
                    ncol = 2, nrow = 3, legend = "top",common.legend = TRUE)
```


### Session 4

```{r, echo= FALSE, message=FALSE, warning=FALSE, fig.width=9, fig.height=9}

P1 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T4S4P1_B, color = "Belief"))+ geom_point(aes(y = T4S4P1_B, color = "Belief")) + 
  geom_line(aes(y = T4S4P1_i, color = "Inform")) + geom_point(aes(y = T4S4P1_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 1")

P2 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T4S4P2_B, color = "Belief"))+ geom_point(aes(y = T4S4P2_B, color = "Belief")) + 
  geom_line(aes(y = T4S4P2_i, color = "Inform")) + geom_point(aes(y = T4S4P2_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 2")

P3 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T4S4P3_B, color = "Belief"))+ geom_point(aes(y = T4S4P3_B, color = "Belief")) + 
  geom_line(aes(y = T4S4P3_i, color = "Inform")) + geom_point(aes(y = T4S4P3_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 3")

P4 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T4S4P4_B, color = "Belief"))+ geom_point(aes(y = T4S4P4_B, color = "Belief")) + 
  geom_line(aes(y = T4S4P4_i, color = "Inform")) + geom_point(aes(y = T4S4P4_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 4")

P5 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T4S4P5_B, color = "Belief"))+ geom_point(aes(y = T4S4P5_B, color = "Belief")) + 
  geom_line(aes(y = T4S4P5_i, color = "Inform")) + geom_point(aes(y = T4S4P5_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 5")

P6 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T4S4P6_B, color = "Belief"))+ geom_point(aes(y = T4S4P6_B, color = "Belief")) + 
  geom_line(aes(y = T4S4P6_i, color = "Inform")) + geom_point(aes(y = T4S4P6_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 6")

ggarrange(P1, P2,P3,P4,P5,P6,
                    ncol = 2, nrow = 3, legend = "top",common.legend = TRUE)
```


### Session 5

```{r, echo= FALSE, message=FALSE, warning=FALSE, fig.width=9, fig.height=9}

P1 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T4S5P1_B, color = "Belief"))+ geom_point(aes(y = T4S5P1_B, color = "Belief")) + 
  geom_line(aes(y = T4S5P1_i, color = "Inform")) + geom_point(aes(y = T4S5P1_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 1")

P2 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T4S5P2_B, color = "Belief"))+ geom_point(aes(y = T4S5P2_B, color = "Belief")) + 
  geom_line(aes(y = T4S5P2_i, color = "Inform")) + geom_point(aes(y = T4S5P2_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 2")

P3 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T4S5P3_B, color = "Belief"))+ geom_point(aes(y = T4S5P3_B, color = "Belief")) + 
  geom_line(aes(y = T4S5P3_i, color = "Inform")) + geom_point(aes(y = T4S5P3_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 3")

P4 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T4S5P4_B, color = "Belief"))+ geom_point(aes(y = T4S5P4_B, color = "Belief")) + 
  geom_line(aes(y = T4S5P4_i, color = "Inform")) + geom_point(aes(y = T4S5P4_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 4")

P5 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T4S5P5_B, color = "Belief"))+ geom_point(aes(y = T4S5P5_B, color = "Belief")) + 
  geom_line(aes(y = T4S5P5_i, color = "Inform")) + geom_point(aes(y = T4S5P5_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 5")

P6 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T4S5P6_B, color = "Belief"))+ geom_point(aes(y = T4S5P6_B, color = "Belief")) + 
  geom_line(aes(y = T4S5P6_i, color = "Inform")) + geom_point(aes(y = T4S5P6_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 6")

ggarrange(P1, P2,P3,P4,P5,P6,
                    ncol = 2, nrow = 3, legend = "top",common.legend = TRUE)
```

### Session 6

```{r, echo= FALSE, message=FALSE, warning=FALSE, fig.width=9, fig.height=9}

P1 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T4S6P1_B, color = "Belief"))+ geom_point(aes(y = T4S6P1_B, color = "Belief")) + 
  geom_line(aes(y = T4S6P1_i, color = "Inform")) + geom_point(aes(y = T4S6P1_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 1")

P2 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T4S6P2_B, color = "Belief"))+ geom_point(aes(y = T4S6P2_B, color = "Belief")) + 
  geom_line(aes(y = T4S6P2_i, color = "Inform")) + geom_point(aes(y = T4S6P2_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 2")

P3 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T4S6P3_B, color = "Belief"))+ geom_point(aes(y = T4S6P3_B, color = "Belief")) + 
  geom_line(aes(y = T4S6P3_i, color = "Inform")) + geom_point(aes(y = T4S6P3_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 3")

P4 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T4S6P4_B, color = "Belief"))+ geom_point(aes(y = T4S6P4_B, color = "Belief")) + 
  geom_line(aes(y = T4S6P4_i, color = "Inform")) + geom_point(aes(y = T4S6P4_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 4")

P5 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T4S6P5_B, color = "Belief"))+ geom_point(aes(y = T4S6P5_B, color = "Belief")) + 
  geom_line(aes(y = T4S6P5_i, color = "Inform")) + geom_point(aes(y = T4S6P5_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 5")

P6 = ggplot(data=subjects_b_i, aes(x=period)) + 
  geom_line(aes(y = T4S6P6_B, color = "Belief"))+ geom_point(aes(y = T4S6P6_B, color = "Belief")) + 
  geom_line(aes(y = T4S6P6_i, color = "Inform")) + geom_point(aes(y = T4S6P6_i, color = "Inform"))+
      theme(legend.title = element_blank())+ 
  scale_x_continuous(name = "Period", breaks = seq(0, 15, by = 1)) +
  scale_y_continuous(name = "Prices")  +
  ggtitle("Player 6")

ggarrange(P1, P2,P3,P4,P5,P6,
                    ncol = 2, nrow = 3, legend = "top",common.legend = TRUE)
```








